---
title: "8.NoSQL Data Storage & Retrieval using MongoDB"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the Bird Strikes file into BS
```{r}
library(mongolite)
BS <- read.csv("Bird Strikes.csv")
head(BS)
```

Inserting the data in MongoDB
```{r}
mongoBS <- mongo("BS")
mongoBS$insert(BS)
```

Exporting the file named BS.txt
```{r}
mongoBS$export(file("BS.txt"))
```

Obtaining distinct airport names
```{r}
distinct <- mongoBS$distinct("AirportName")
head(distinct)
```

Total rows with origin state as New Jersey
```{r}
J <- mongoBS$count('{"OriginState":"New Jersey"}')
J
```

Getting data with ConditionsPreceipitation is fog and has RecordID in desceding order.
```{r}
CPF <- mongoBS$find('{"ConditionsPrecipitation":"Fog"}', sort= '{"RecordID":-1}')
head(CPF)
```

For AircraftAirlineOROperator as American Airlines fetching columns RecordID, OriginState, AircraftAirlineOROperator and AirportName
```{r}
AA <- mongoBS$find('{"AircraftAirlineOROperator":"AMERICAN AIRLINES"}', fields = '{"RecordID":1, "OriginState":1, "AircraftAirlineOROperator":1, "AirportName":1}')
head(AA)
```

For AircraftAirlineOROperator as Continental Airlines fetching columns RecordID, OriginState, AircraftAirlineOROperator and AirportName
```{r}
CA<- mongoBS$find('{"AircraftAirlineOROperator":"CONTINENTAL AIRLINES"}', fields = '{"RecordID":1, "OriginState":1, "AircraftAirlineOROperator":1, "AirportName":1}')
head(CA)
```
