---
title: "Shetty_S_10"
author: "Sooraj Shetty"
date: "11/14/2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 10

Reading the birdstrikes database
```{r}
bs <- read.csv("Bird Strikes.csv",sep = ",")
head(bs)
```

Adding additional columns for the data base
```{r}
bs$AircraftNo<-seq.int(nrow(bs))
bs$AirportNo<-seq.int(nrow(bs))
bs$LocENo<-seq.int(nrow(bs))
bs$CostNo<-seq.int(nrow(bs))
bs$EffectONo<-seq.int(nrow(bs))
bs$ConditionNo<-seq.int(nrow(bs))
bs$EffectNo<-seq.int(nrow(bs))
```

Creating data frames for the database
Data frame for aircrafts
```{r}
Aircraft <- data.frame(bs$AircraftNo,bs$Aircraft..Type,bs$Aircraft..Airline.Operator,bs$Aircraft..Make.Model,bs$Aircraft..Number.of.engines.,bs$Altitude.bin)
```

Data frame for airports
```{r}
Airport <- data.frame(bs$AirportNo,bs$Airport..Name,bs$Origin.State)
```

Data frame for location enroute
```{r}
LocationEnroute <- data.frame(bs$LocENo,bs$Location..Nearby.if.en.route)
```

Data frame for effect (wildlife)
```{r}
EffectW <- data.frame(bs$EffectNo,bs$Wildlife..Number.struck,bs$Wildlife..Size,bs$Wildlife..Species,bs$Remains.of.wildlife.collected.,bs$Record.ID)
```

Data frame for effect (flights)
```{r}
EffectF <- data.frame(bs$Record.ID,bs$Effect..Impact.to.flight,bs$EffectONo,bs$When..Phase.of.flight,bs$LocENo,bs$FlightDate,bs$Effect..Indicated.Damage,bs$Speed..IAS..in.knots,bs$Feet.above.ground,bs$Remarks,bs$When..Time..HHMM,bs$Reported..Date,bs$Pilot.warned.of.birds.or.wildlife.,bs$ConditionNo)
```

Data frame for effect (other)
```{r}
EffectO <- data.frame(bs$EffectONo,bs$Effect..Other)
```

Data frame for cost
```{r}
Cost <- data.frame(bs$CostNo,bs$Record.ID,bs$Cost..Repair..inflation.adj.,bs$Cost..Total..)
```

Data frame for conditions
```{r}
Condition <- data.frame(bs$ConditionNo,bs$Conditions..Sky,bs$Conditions..Precipitation)
```

Calling necessary libraries
```{r}
library(sqldf)
library(proto)
library(gsubfn)
```

Connecting to SQLite
```{r}
db <- dbConnect(SQLite(), dbname="bs.sqlite")
```

Creating tables for the database
```{r}
dbWriteTable(conn = db, name = "Aircraft", value = Aircraft, row.names = FALSE)
dbWriteTable(conn = db, name = "Airport", value = Airport, row.names = FALSE)
dbWriteTable(conn = db, name = "LocationEnroute", value = LocationEnroute, row.names = FALSE)
dbWriteTable(conn = db, name = "EffectW", value = EffectW, row.names = FALSE)
dbWriteTable(conn = db, name = "EffectF", value = EffectF, row.names = FALSE)
dbWriteTable(conn = db, name = "EffectO", value = EffectO, row.names = FALSE)
dbWriteTable(conn = db, name = "Cost", value = Cost, row.names = FALSE)
dbWriteTable(conn = db, name = "Condition", value = Condition, row.names = FALSE)
```

Listing tables in database
```{r}
dbListTables(db)
```

Listing columns in a table in the database
```{r}
dbListFields(db, "Aircraft")
dbListFields(db, "Airport")
dbListFields(db, "Condition")
dbListFields(db, "Cost")
dbListFields(db, "EffectF")
dbListFields(db, "EffectO")
dbListFields(db, "EffectW")
dbListFields(db, "LocationEnroute")
```

Fetching data from a table in the database
```{r}
dbReadTable(db, "Aircraft")
dbReadTable(db, "Airport")
dbReadTable(db, "Condition")
dbReadTable(db, "Cost")
dbReadTable(db, "EffectF")
dbReadTable(db, "EffectO")
dbReadTable(db, "EffectW")
dbReadTable(db, "LocationEnroute")
```

Select statement to display data from LocationEnroute table
```{r}
dbGetQuery(conn = db, "SELECT * FROM LocationEnroute")
```

Select statement to display data from EffectF table
```{r}
dbGetQuery(conn = db, "SELECT * FROM EffectF")
```
